The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
rephrased Blackbody model to be more stylistically consistent w/other text

The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed flux densities in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).

>>>>

The \package{astropy.modeling} subpackage now supports the representation,
evaluation, and fitting of models using \texttt{Quantity} objects, which attach
units to scalar values or arrays of values. In practice, this means that one
can, for example, fit a model to data with units and get parameters that also
have units out, or initialize a model with parameters with units and evaluate
it using input values with different but equivalent units. For example, the
blackbody model (\texttt{BlackBody1D}) can be used to fit observed flux
densities in a variety of units and as a function of different units of
spectral coordinates (e.g., wavelength or frequency).
